Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
moved some pieces from Experimental Paradigm into new Approach section per MO suggestion

@@

\section{Experimental paradigm}

Section explains space of measures to explore

\begin{itemize}
\item F-measure over various bags of components of parse tree

  [ Figure describing Sparseval-ish variant ]

\item Listing possible component valences
  \begin{itemize}
  \item dependent + labeled link + head 
  \item outbound only (dependent +
    label)
  \item inbound only (label + head)
  \item word-word (skipping label)
  \end{itemize}
  \begin{itemize}
  \item 1-grams
  \item 2-grams
  \item \ldots{}
  \end{itemize}

@@

>>>>

OVERVIEW OF THE REST OF THE PAPER

@@

\section{Approach}

Outline of big idea here.

\begin{itemize}
\item comparison of various bags of components of parse tree
  [ Figure describing Sparseval-ish variant ]

  Like sparseval: basic unit is labeled dependency pair

@@

\item elements may be combined in various ways: single-bag F, combination of p,r
  measures (evenly, on analogy with BLEU)... or we might weight
  different combinations

\end{itemize}
\section{Experimental paradigm}

Section explains space of measures to explore, mean-normalization

\begin{itemize}
\item Listing possible component valences
  \begin{itemize}
  \item dependent + labeled link + head 
  \item outbound only (dependent +
    label)
  \item inbound only (label + head)
  \item word-word (skipping label)
  \end{itemize}
  \begin{itemize}
  \item 1-grams
  \item 2-grams
  \item \ldots{}
  \end{itemize}
